A systematic search for transiting planets in the \KT\ data

### 2015-02-16 ms.tex
adding some URLs

@@

The starting point for analysis is the raw pixel data.
We download the full set of 21,703 target pixel files for \KT's Campaign~1
from MAST\footnote{\url{https://archive.stsci.edu/k2/}}.
We extract photometry using fixed approximately circular, binary apertures of
varying sizes centered on the predicted location of the target star based on
the world coordinate system.
For each target, we use a set of apertures ranging in radius from 1 to 5
pixels (in steps of 0.5 pixels).
Following \citet{Vanderburg:2014}, we choose the aperture size with the
minimum CDPP \citep{cdpp} with a 6 hour window.\footnote{Note that although we
chose a specific aperture for each star, photometry for every aperture radius
is available online at \dfmtodo{some URL}.}

@@

One key realization that is also exploited by the official \kepler\ pipeline
is that the systematic trends caused by pointing shifts and other instrumental
effects are shared---with different signs and weights---by all the stars on
the focal plane.
To capitalize on this, the \pdc\ component of the \kepler\ pipeline
removes any trends from the light curves that can be fit using a linear
combination of a small number of ``co-trending basis vectors''.
This basis of trends was found by running Principal Component Analysis (PCA)
on a large set of (filtered) light curves and extracting the top few ($\sim 4$)
components \citep{pdc1, pdc2}.
Similarly, we ran PCA on the full set of our own generated \KT\ Campaign~1
light curves to determine a basis of representative trends but, unlike \pdc,
we retain and use a large number of these components ($150$).
For clarity, we will refer to our basis as a set of ``eigen light curves''
(ELCs) and the full set is made available online (\dfmtodo{SOMEURL}).
The top ten ELCs for Campaign~1 are shown in \Fig{pca}.

@@

The periodic search procedure returned three signals per target so this gave
an initial list of 65,109 candidates.
The vast majority of these signals are not induced by a transiting planet;
there are many false positives.
Therefore to reduce the search space, we estimate the signal-to-noise of each
candidate by comparing the peak height to a robust estimate of variance in
\TIC\ values across period.
This is not the same criterion used to select the initial three peaks but we
find that it produces a more complete and pure sample.
A cut in this quantity can reject most variable stars and low signal-to-noise
candidates that can't be reliably recovered from the data.
Figure~\dfmtodo{SOMEFIGURE} shows the distribution of signal-to-noise for a set of
injections and compares it to the distribution of false candidates that are
proposed by the pipeline.
To minimize contamination from false alarms but maximize our sensitivity, we
choose a threshold of 15.
We also find that the signals with periods $\lesssim 4$ days are strongly
contaminated by false alarms.
This might be because of the fact that our independence assumption
(\eqalt{indtran}) breaks down at these short periods.
Therefore, we discard all signals with periods shorter than 4 days.
After these cuts, 741 candidates remain; we examine these signals by hand.
The full list of peaks and their relevant meta data is available online at
\dfmtodo{SOMEURL}.

@@

After our initial cuts on the candidate list, the majority of signals are
still false alarms mostly due to variable stars or single outlying data
points.
It should be possible to construct a more robust machine vetting algorithm
that discards these samples without missing real transits but for the purposes
of this \paper, we simply inspect the light curve for each of the 741
candidates \emph{by hand} to discard signals that are not convincing transits.
The results of this vetting can be seen online at \dfmtodo{SOMEURL}.

@@

\figurename s~\figref{completeness} and~\figref{completeness-mag} show the
fraction of recovered signals as a function of the physical parameters of the
injection and the magnitude of the star in the \kepler\ bandpass as reported
in the Ecliptic Plane Input Catalog
(EPIC\footnote{\url{http://archive.stsci.edu/k2/epic.pdf}}).
As expected, the shallower transits at longer periods are recovered less
robustly and all signals become harder to detect for fainter stars.
It is worth noting that these \figurename s are projections (or
marginalizations) of a higher dimensional measurement of the recovery rate as
a function of all of the input parameters.
For example, this detection efficiency map is conditioned on our assumptions
about the eccentricity distribution of planets and it is marginalized over the
empirical distribution of stellar parameters.
It is possible to relax this assumption and apply different distributions by
re-weighting the simulations used to generate this figure.
Therefore, alongside this \paper, we publish the full list of injection
simulations\footnote{SOMEURL} to be used for population inference (occurrence
rate measurements).

@@

The remaining signals are caused by eclipsing binaries (EBs).
In most cases, the search reports the secondary eclipse as a candidate and in
a few very high signal-to-noise cases, the period reported by the pipeline is
incorrect and multiple candidates correspond to the same transit.
It is important to note, however, that the choices made in the search were
heuristically tuned to find planets, not binaries, so our results are not
complete or exhaustive, especially at short orbital periods.
There are other methods specifically tuned to find EBs in \KT\
\citep[such as][]{Armstrong:2014, Armstrong:2015} and these catalogs contain
our full sample of EBs and more.

For the planet candidates, we perform a full physical transit fit to the light
curve.
To do this fit, we use Markov Chain Monte Carlo \citep[MCMC;][]{emcee} to
sample from the posterior probability for the stellar and planetary
parameters taking limb darkening and integration time into account.
In this fit, we continue to model the trends in the data as a linear
combination of the 150 ELCs but, at this point, we combine this with a
realistic light curve model \citet{ma, kipping-ld}.
Even though we have no constraints on the stellar parameters, we also sample
over a large range in stellar mass and radius so that future measurements can
be applied by re-weighting the published samples.
In \tab{cand} we list the sample quantiles for the observable quantities and
the full chains are available electronically at \dfmtodo{some URL}.
\fig{candidates} shows the observed distribution of planet candidates in the
catalog.

@@

We have searched the \KT\ Campaign~1 data set for exoplanet transit signals.
Our search is novel because it includes a very flexible systematics model,
which is fit simultaneously with the exoplanet signals of interest (and
marginalized out).
By this method, we find 36 transiting exoplanets, which we have vetted by both
automatically and manually and characterized by probabilistic modeling.
The candidates are listed in \tab{cand} and posterior distributions of planet
candidate properties are available at \dfmtodo{thisurl}.

@@

>>>>

\newcommand{\datareleaseurl}{{\url{http://bbq.dfm.io/ketu}}}

@@

The starting point for analysis is the raw pixel data.
We download the full set of 21,703 target pixel files for \KT's Campaign~1
from MAST\footnote{\url{https://archive.stsci.edu/k2/}}.
We extract photometry using fixed approximately circular, binary apertures of
varying sizes centered on the predicted location of the target star based on
the world coordinate system.
For each target, we use a set of apertures ranging in radius from 1 to 5
pixels (in steps of 0.5 pixels).
Following \citet{Vanderburg:2014}, we choose the aperture size with the
minimum CDPP \citep{cdpp} with a 6 hour window.\footnote{Note that although we
chose a specific aperture for each star, photometry for every aperture radius
is available online: \datareleaseurl.}

@@

One key realization that is also exploited by the official \kepler\ pipeline
is that the systematic trends caused by pointing shifts and other instrumental
effects are shared---with different signs and weights---by all the stars on
the focal plane.
To capitalize on this, the \pdc\ component of the \kepler\ pipeline
removes any trends from the light curves that can be fit using a linear
combination of a small number of ``co-trending basis vectors''.
This basis of trends was found by running Principal Component Analysis (PCA)
on a large set of (filtered) light curves and extracting the top few ($\sim 4$)
components \citep{pdc1, pdc2}.
Similarly, we ran PCA on the full set of our own generated \KT\ Campaign~1
light curves to determine a basis of representative trends but, unlike \pdc,
we retain and use a large number of these components ($150$).
For clarity, we will refer to our basis as a set of ``eigen light curves''
(ELCs) and the full set is made available online\footnote{\datareleaseurl}.
The top ten ELCs for Campaign~1 are shown in \Fig{pca}.

@@

The periodic search procedure returned three signals per target so this gave
an initial list of 65,109 candidates.
The vast majority of these signals are not induced by a transiting planet;
there are many false positives.
Therefore to reduce the search space, we estimate the signal-to-noise of each
candidate by comparing the peak height to a robust estimate of variance in
\TIC\ values across period.
This is not the same criterion used to select the initial three peaks but we
find that it produces a more complete and pure sample.
A cut in this quantity can reject most variable stars and low signal-to-noise
candidates that can't be reliably recovered from the data.
To minimize contamination from false alarms but maximize our sensitivity, we
choose a threshold of 15.
We also find that the signals with periods $\lesssim 4$ days are strongly
contaminated by false alarms.
This might be because of the fact that our independence assumption
(\eqalt{indtran}) breaks down at these short periods.
Therefore, we discard all signals with periods shorter than 4 days.
After these cuts, 741 candidates remain; we examine these signals by hand.
The full list of peaks and their relevant meta data is available online
at\footnote{\datareleaseurl}.

@@

After our initial cuts on the candidate list, the majority of signals are
still false alarms mostly due to variable stars or single outlying data
points.
It should be possible to construct a more robust machine vetting algorithm
that discards these samples without missing real transits but for the purposes
of this \paper, we simply inspect the light curve for each of the 741
candidates \emph{by hand} to discard signals that are not convincing transits.
The results of this vetting can be seen online\footnote{\datareleaseurl}.

@@

\figurename s~\figref{completeness} and~\figref{completeness-mag} show the
fraction of recovered signals as a function of the physical parameters of the
injection and the magnitude of the star in the \kepler\ bandpass as reported
in the Ecliptic Plane Input Catalog
(EPIC\footnote{\url{http://archive.stsci.edu/k2/epic.pdf}}).
As expected, the shallower transits at longer periods are recovered less
robustly and all signals become harder to detect for fainter stars.
It is worth noting that these \figurename s are projections (or
marginalizations) of a higher dimensional measurement of the recovery rate as
a function of all of the input parameters.
For example, this detection efficiency map is conditioned on our assumptions
about the eccentricity distribution of planets and it is marginalized over the
empirical distribution of stellar parameters.
It is possible to relax this assumption and apply different distributions by
re-weighting the simulations used to generate this figure.
Therefore, alongside this \paper, we publish the full list of injection
simulations\footnote{\datareleaseurl} to be used for population inference
(occurrence rate measurements).

@@

The remaining signals are caused by eclipsing binaries (EBs) with visible
secondary eclipses.
In most cases, the search reports the secondary eclipse as a candidate and in
a few very high signal-to-noise cases, the period reported by the pipeline is
incorrect and multiple candidates correspond to the same transit.
It is important to note, however, that the choices made in the search were
heuristically tuned to find planets, not binaries, so our results are not
complete or exhaustive, especially at short orbital periods.
There are other methods specifically tuned to find EBs in \KT\
\citep[such as][]{Armstrong:2014, Armstrong:2015} and these catalogs contain
our full sample of EBs and more.

For the planet candidates, we perform a full physical transit fit to the light
curve.
To do this fit, we use Markov Chain Monte Carlo \citep[MCMC;][]{emcee} to
sample from the posterior probability for the stellar and planetary
parameters taking limb darkening and integration time into account.
In this fit, we continue to model the trends in the data as a linear
combination of the 150 ELCs but, at this point, we combine this with a
realistic light curve model \citet{ma, kipping-ld}.
Even though we have no constraints on the stellar parameters, we also sample
over a large range in stellar mass and radius so that future measurements can
be applied by re-weighting the published samples.
In \tab{cand} we list the sample quantiles for the observable quantities and
the full chains are available electronically\footnote{\datareleaseurl}.
\fig{candidates} shows the observed distribution of planet candidates in the
catalog.

@@

We have searched the \KT\ Campaign~1 data set for exoplanet transit signals.
Our search is novel because it includes a very flexible systematics model,
which is fit simultaneously with the exoplanet signals of interest (and
marginalized out).
By this method, we find 36 transiting exoplanets, which we have vetted by both
automatically and manually and characterized by probabilistic modeling.
The candidates are listed in \tab{cand} and posterior distributions of planet
candidate properties are available\footnote{\datareleaseurl}.

@@

As a supplement to this \paper, we make all the results, data products, and
MCMC chains available at \datareleaseurl.
The \LaTeX\ source for this \paper, complete with the full revision history,
is available at \url{http://github.com/dfm/k2-paper} and the pipeline
implementation is available at \url{http://github.com/dfm/ketu} under the MIT
open-source software license.
This code and a lot of computation time are all that is needed to reproduce
the \figurename s in this \paper.
